Discovering Focused Microgenre Communities

### 2023-08-04 main.tex

\begin{figure}[ht!]
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
     \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
        \caption{Edge similarity matrix from toy example.}
        \label{fig:toy-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
        \caption{Edge distance matrix from toy example.}
        \label{fig:toy-dis}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy-ex}
 \end{figure}

@@

\begin{figure}[ht!]
    \centering    
    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-metal.png}
    \caption{}
    \label{tab:reg-metal}
\end{figure}

@@

\begin{figure}[ht!]
    \centering    \includegraphics[width=1.0\textwidth]{Plots/Demog/micro-by-age-metal.png}
    \caption{}
    \label{fig:age-metal}
\end{figure}

@@

\begin{figure}[ht!]
    \centering    
    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-latin.png}
    \caption{}
    \label{tab:reg-latin}
\end{figure}

@@

\begin{figure}[ht!]
    \centering    \includegraphics[width=1.0\textwidth]{Plots/Demog/micro-by-age-latin.png}
    \caption{}
    \label{fig:age-salsa}
\end{figure}

>>>>

\begin{figure}[ht!]
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
        \caption{Edge similarity matrix from toy example.}
        \label{fig:toy-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
        \caption{Edge distance matrix from toy example.}
        \label{fig:toy-dis}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy-ex}
 \end{figure}

@@

\begin{figure}[ht!]
     \begin{subfigure}[b]{1.0\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Tabs/reg-tab-metal.png}
        \caption{}
        \label{tab:reg-metal}
    \end{subfigure} \\
     \begin{subfigure}[b]{1.0\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Tabs/reg-tab-latin.png}
        \caption{}
        \label{tab:reg-latin}
    \end{subfigure}
\end{figure}

@@

\begin{figure}[ht!]
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-metal.png}
        \caption{}
        \label{fig:age-metal}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-latin.png}
        \caption{}
        \label{fig:age-latin}
    \end{subfigure}
\end{figure}

@@

@@
